### 2010-03-31 papers/icfp-2010-desc/paper_discussion.tex
Desc@ICFP: fix Generic Haskell related work.

Our approach also support the Generic
Haskell~\cite{hinze:generic-haskell} model. This model, based on
type-indexed data types, enables computing new data-types from
others. This is natural in our system, as data-types descriptions are
first-class.

>>>>

We share with Generic Haskell the \emph{type-indexed data type}
approach~\cite{hinze:generic-haskell}, as exemplified by the free
monad construction: from data-type, we can compute new data-types and
equip them with their structure. Generic Haskell also features
\emph{generic views}~\cite{holdermans:generic-view}, transparently
transforming the structure of data-type definitions, to ease the
implementation of generic functions over them. Views in
dependently-typed system are widely
used~\cite{mcbride.mckinna:view-from-the-left}. Unlike in Generic
Haskell, we do not have to modify the compiler to develop views on
data-types: we can massage description codes from inside the language
and present them as a standard view. An example of such operation is
the tagged descriptions, presenting data-types under a particular
angle.

Unlike Generic Haskell, we do not support polykinded
programming~\cite{hinze:polytypic-polykinded}. Our descriptions are
limited to endofunctor on $\Set$ and $\Set^I$. While it is possible to
\emph{encode} higher-kinded data-types in our setting, we do not plan
to adopt this strategy. Rather, as future work, we plan to extend our
universe to capture higher-kinded definitions and generic functions
over them. For the same reason, arity-generic
programming~\cite{weirich:arity-generic} is out of reach of our
current presentation.
